---
title: "LabHw4"
author: "Neelakshi Soni"
date: "February 4, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### tiff

```{r tiff}
library(ggplot2)
library(grid)
plot.diamonds <- ggplot(diamonds, aes(clarity, fill = cut)) + geom_bar() +
  theme(axis.text.x = element_text(angle=70, vjust=0.5))
plot.diamonds
ggsave("diamonds.tif",device="tiff", dpi = 600)
```

### ggpubr to use ggarrange as key function/package

```{r ggpubr}
library(ggpubr)
ggarrange(plot.diamonds,ggarrange(plot.diamonds, plot.diamonds, nrow = 2, labels = c("B", "C")), ncol = 2,labels = "A")
```

### to flip the col/row layout

```{r ggpubr}
library(ggpubr)
ggarrange(plot.diamonds,ggarrange(plot.diamonds, plot.diamonds, ncol = 2, labels = c("B", "C")), nrow = 2,labels = "A")
```

### egg using gtable_frame as the key function/package

```{r egg}
library(egg)
g1 <- ggplotGrob(plot.diamonds)
fg1 <- gtable_frame(g1, debug = T)
fg12 <- gtable_frame(gtable_rbind(fg1,fg1),
                     width = unit(1,"null"),
                     height = unit(2,"null"))
fg3 <- gtable_frame(g1, width = unit(1,"null"), height = unit(1,"null"), debug = T) 
grid.newpage()
combined <- gtable_cbind(fg3,fg12)
grid.draw(combined)
grid.remove(axis, grep = T, global = T)
```

The only thing I find weird about the packages is the huge overlap between the them.

### littler

```{r littler}
library(tidyverse)
readr::write_delim(diamonds,"diamonds.txt")
```

### R script

```{r scripting}
#!/usr/bin/Rscript
library(methods)
require(optparse)
require(ggplot2)


option_list = list(
              make_option(c("--infile"), default = NULL,action = "store_true",
              help = "dataset file name",dest = "infile", type = "character"),
          make_option(c("--xaxis"), default = "clarity",action = "store_true",
              help = "dataset x axis",dest = "xaxis", type = "character"),
          make_option(c("--filler"), default = "cut",action = "store_true",
              help = "dataset filler values",dest = "filler", type = "character"),
          make_option(c("--outfile"), default = NULL,action = "store_true",
              help = "dataset outfile name",dest = "outfile", type = "character")
);

opt_parser = OptionParser(option_list=option_list);
opt = parse_args(opt_parser);


data <- read.table(opt$infile, header=TRUE)
newdata <- data.frame(x=data[,opt$xaxis],y = data[,opt$filler])
p <- ggplot(newdata, aes(x=x, fill=y))+ geom_bar()+
    theme(axis.text.x=element_text(angle=70,vjust=0.5))

ggsave(paste0(opt$outfile,".png"),device="png",dpi=600)
```

```{bash command_line}
Rscript ./littler_script1.R --infile diamonds.txt --outfile diamonds --xaxis clarity --filler cut 
chmod +x ./littler_script1.R
./littler_script1.R --infile diamonds.txt --outfile diamonds --xaxis clarity --filler cut
```

### reticulate

```{r reticulate}
library(reticulate)
use_python("/usr/bin/python3")
pd <- import("pandas", convert=F)
x = data.frame(x=rnorm(100),y=rnorm(100))
y = pd$DataFrame(r_to_py(x))
z = py_to_r(y$describe())
print(z)
```

### getting rid of convert=F and py_to_r

```{r reticulate}
pd <- import("pandas")
x = data.frame(x=rnorm(100),y=rnorm(100))
y = pd$DataFrame(x)
z = (y$describe())
print(z)
```

It doesn't seem to work and I believe its to do with the object conversions. When a python API requires a list and instead a single element R vector is passed, it would get converted to python scalar.

### excuting python in R


```{r python_execute}
library(reticulate)
use_python("/usr/bin/python3")
repl_python()
```

```{python repl_python}
import pandas as pd
x = pd.read_csv("data2.txt",sep=" ")
exit
```

```{r accesing_data}
py$x
```

### external python script

```{python script}
import pandas as pd
file = pd.read_csv("data2.txt", sep= " ")
```

```{r run_external_python}
py_run_file("get_df.py")
x <- py$file
```

### gridspec

```{python plot}

```
