---
title: "LabAssignment1"
author: "Neelakshi Soni"
date: "January 16, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

R Markdown

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(include = FALSE)
```

Chapter 7

1. Creating a small tibble manually

```{r tibble, include=FALSE}
tb <- tibble(x = 1:5, y = x ^ 2) 
```

2. Do exercises 1,2,4,5,6 from this chapter. I have no idea what 3 is about, so it can't be important, right???

a. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame.)

```{r tibble_print}
class(tb)
is.tibble(tb)
print(tb)
print(mtcars)
```
b. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviors cause you frustration? 
df <- data.frame(abc = 1, xyz = "a") 
df$x 
df[, "xyz"] 
df[, c("abc", "xyz")] 

```{r tibble_data.frame, include=FALSE}
df <- data.frame(abc = 1, xyz = "a") 
df$x 
df[, "xyz"] 
df[, c("abc", "xyz")] 

df1 <- tibble(abc = 1, xyz = "a") 
df1$x 
df1[, "xyz"] 
df1[, c("abc", "xyz")] 
```
As seen above Tibbles are data.frames that do less (i.e. they don't change variable names or types, and don't do partial matching) and complain more (e.g. when a column is not initialised). This forces you to confront problems earlier, typically leading to cleaner, more expressive code.

c. Practice referring to nonsyntactic names in the following data frame by: 
i. Extracting the variable called 1. 
ii. Plotting a scatterplot of 1 versus 2. 
iii. Creating a new column called 3, which is 2 divided by 1. 
iv. Renaming the columns to one, two, and three:
annoying <- tibble(  `1` = 1:10,  `2` = `1` * 2 + rnorm(length(`1`)) ) 

```{r tibble_plot}
annoying <- tibble(  `1` = 1:10,  
                     `2` = `1` * 2 + rnorm(length(`1`)) ) 
annoying$`1`
plot(x = annoying$`1`,y = annoying$`2`,
   xlab = "Var 1",
   ylab = "Var 2",
   main = "Scatter Plot"
)
annoying$`3` <- annoying$`2`/annoying$`1` 
names(annoying) <- c("one","two","three")
```
d.  What does tibble::enframe() do? When might you use it? 

enframe() converts named atomic vectors or lists to two-column data frames.For a list, the result will be a nested tibble with a column of type `list`. For unnamed vectors, the natural sequence is used as name column. Coercing a nested list to data frame could be a use of this function.

```{r enframe}
enframe(1:3)
enframe(c(a = 5, b = 7))
```

e. What option controls how many additional column names are printed at the footer of a tibble?

"n_extra" argument in the print command allows to print the number of extra columns with abbreviated information ,if the width is too small for the entire tibble. 

Chapter 8

1. In the first set of chapter questions, do questions 1, 2, 4 and 5.

a. What function would you use to read a file where fields are separated with "|"?

read_delim(file, delim="|") allows us to read files with the delimiter specified as "|".

b. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

The arguments similar between both the functions are col_names, col_types, locale, na, quoted_na,quote, trim_ws, n_max, guess_max, progress, skip_empty_rows.

c. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you'll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame? 
"x,y\n1,'a,b'" 

The following changes will allow for the text to be read correctly
```{r csv}
read_csv("x,y\n1,'a,b'", quote="'")
```
d.  Identify what is wrong with each of the following inline CSV files. What happens when you run the code? 
read_csv("a,b\n1,2,3\n4,5,6") 
read_csv("a,b,c\n1,2\n1,2,3,4") 
read_csv("a,b\n\"1") 
read_csv("a,b\n1,2\na,b") 
read_csv("a;b\n1;3")

For the first one since the third column name is not specified a warning message is generated with 2 passing failures where the third column would not be registered (3,6). For the second command the third column does not have a value assigned to it hence the cell is now has the value "NA" and the third column has the value "4" missing as there is no 4th column. The third command has a closing quote at te end of file which would shoot a warning message and again as there is an empty cell the value filled would be "NA". For the fourth command the column name matched the values assigned which would not throw an error. The values in the last command are seperated by a semi-colon hence the function groups them together.

Chapter 9

1. Exercise 3 in the first set of exercises.

Re-create the plot showing change in cases over time using table2 instead of table1. What do you need to do first?

```{r spread}
tb1 <- spread(tidyr::table2, type, count)
library(ggplot2) 
ggplot(tb1, aes(year, cases)) +  geom_line(aes(group = country), color = "grey50") +  geom_point(aes(color = country))

```

spread(), takes two columns (a key-value pair) and spreads them in to multiple columns, making "long" data wider.

2. Exercise 2 in the second set of exercises

Why does this code fail? table4a %>%  gather(1999, 2000, key = "year", value = "cases")

```{r gather}
table4a %>%  gather(1999, 2000, key = "year", value = "cases")
```
As "1999" and "2000" are nonsyntactic names so we have to surround them in backticks

Chapter 10

1. Exercise 1 in second set of exercises

Add a surrogate key to flights. 

```{r surrogate}
library(nycflights13)
new_flights = mutate(flights, diff_shedule_time = flights$sched_dep_time - flights$dep_time)
```
Difference in minutes between EDT and DT is the surrogate key

2. Exercise 2 in the second set of exercises

Add the location of the origin and destination (i.e., the lat and lon) to flights.

```{r lat_lon}
flights1 = flights %>%  left_join(airports[,-c(2,5:8)], c("origin" = "faa")) %>%  left_join(airports[,-c(2,5:8)], c("dest" = "faa"))
colnames(flights1)[20:23]<-c("lat_org","lon_org","lat_dest","lon_des")
```
