---
title: "labAssignment2"
author: "Neelakshi Soni"
date: "January 17, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R

1. How do you ask if a file exists?

```{r exists}
destfile <- "C:/Users/neela/Desktop/foo.txt"
file.exists(destfile)
```

2. How to you ask if a file is a directory?

```{r isdir}
file.info(destfile)$isdir
```

3. How do you remove (delete) a file?

```{r remove}
file.remove("foo.txt")
```
4. How do you get the size of a file?

```{r size}
file.info(destfile)$size
```
5. How do you get all the file names matching a pattern?

```{r pattern}
list.files(path = "C:/Users/neela/Desktop/Lindsay",pattern='*\\.csv')
```
6. How do you get all the file names matching a pattern recursively?

```{r pattern_recursive}
list.files(path = "C:/Users/neela/Desktop/Lindsay",pattern='*\\.csv', recursive=T, full.names = T)
```

7. How do you open gzip-compressed files for reading and for writing?

```{r gzip}
gzfile("test.dat.gz", open = "rt") # text mode
gzfile("test.dat.gz", open = "wt") # text mode
gzfile("test.dat.gz", open = "r+b") # both read and write
gzfile("test.dat.gz", open = "rb") # binary mode
gzfile("test.dat.gz", open = "wb") # binary mode
```

## Python

1. How do you ask if a file exists?

```{python exists}
import os.path
os.path.exist("C:/Users/neela/Desktop/Lindsay/normalised nanostring/dexp.R")
```

2. How to you ask if a file is a directory?

```{python isdir}
import os.path
os.path.isdir("C:/Users/neela/Desktop/Lindsay/normalised nanostring")
```

3. How do you remove (delete) a file?

```{python remove}
import os.path
os.remove("/tmp/<file_name>.txt")
```

4. How do you get the size of a file?

```{python size}
import os
os.path.getsize("C:/Users/neela/Desktop/Lindsay/normalised nanostring/dexp.R")
```

5. How do you get all the file names matching a pattern?

```{python pattern}
import glob
glob.glob("*.csv")
```

6. How do you get all the file names matching a pattern recursively?

```{python pattern_recursive}
import glob
for filename in glob.iglob('*/*.csv', recursive=True): print(filename)
```

7. How do you get an iterator to all files matching a pattern, as opposed to returning a potentially huge list?

```{python  iterator}
import glob
my_list = glob.glob("*.csv")
my_iter = iter(my_list)
print(next(my_iter))
```

8. How do you open gzip-compressed files for reading and for writing?

```{python gzip}
import gzip
with gzip.open('file.txt.gz', 'rb') as f:
    file_content = f.read()
import gzip
content = "Lots of content here"
with gzip.open('file.txt.gz', 'wb') as f:
    f.write(content)
```
